Deterministic Scheduling of Periodic Messages in a Network

### 2017-06-22 article/article.tex
figures notations

@@

\section{Introduction}

@@

This problem may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just avoid deadlocks, moreover the periodicity is not considered in wormhole problems. Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}. Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are also $\NP$-complete. The only model which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but is not expressive enough to capture our problem.

@@

@@

      \begin{center}
      \includegraphics[scale=0.3]{rrh.png}
      \end{center}

@@

       \begin{center}
      \includegraphics[scale=0.17]{BBU2.png}
      \end{center}

@@

       \begin{center}
	 \scalebox{0.7}{
\begin{tikzpicture}

@@

  \node[draw,circle] (cs) at (2, 2) {$c_s$}; 
  \node[draw,circle] (ct) at (6, 2) {$c_t$};

  \Edge(s1)(cs)
  \Edge(s2)(cs)
  \Edge(s3)(cs)

  \Edge(ct)(t1)
  \Edge(ct)(t2)
  \Edge(ct)(t3)

@@

	Finally, the time to build this assignment is dominated by the sorting of the routes from the longest to the shortest and is thus in $O(n\log(n)$.
     \end{proof}

\todo{Une remarque sur le fait que la complexitÈ dÈpend sans doute du nombre de valeurs diffÈrentes sur les arcs et pas du nombre de routes.}

>>>>

\renewcommand{\thefootnote}{\*}

@@

\footnote{This work is partialy supported by the french  ANR project N-GREEN.}
\section{Introduction}

@@

 Thus in this article, we work on latency and periodicity constraints in fron- thaul. The best current solution is to rely on an almost full optical approach, where each end-points (RRH on one side, BBU on the other side) are connected through direct fiber or full optical switches [7]. This architecture is very ex- pensive and hardly scales in the case of a mobile network composed of about 10,000 base stations. It is then needed to find a solution to offer low latency over commoditized packet based networks. Indeed, dynamical optical bypass and dynamical management of the emission should be considered to guarantee latency constraints, as it is considered in the french ANR project N-GREEN. This project proposes a new type of switching/routing node and a specific net- work architecture exploiting WDM packets thanks to a new generation of optical add/drop multiplexers (WSADM: WDM slotted add/drop multiplexer). These packets having a fixed duration close to 1?s are transported in a transparent way, to better exploit the switching matrix of the node; their headers will be transported over one dedicated wavelength at a lower bit rate, to reduce the physical constraints of the electronic processing and scheduler.

The problem we thus focus on here may look like wormhole problems~\cite{cole1996benefit}, but here we want to minimize the time lost in buffers and not just avoid deadlocks, moreover the periodicity is not considered in wormhole problems. Several graph colorings have been introduced to model similar problems such as the allocation of frequencies~\cite{borndorfer1998frequency}, bandwidths~\cite{erlebach2001complexity} or routes~\cite{cole1996benefit} in a network or train schedules~\cite{strotmann2007railway}. Unfortunately, they do not take into account the periodicity of the scheduling and the associated problems are also $\NP$-complete. The only model which incorporates some periodicity is the circular coloring~\cite{zhou2013multiple, zhu2001circular,zhu2006recent} but is not expressive enough to capture our problem.

@@

      The following table summarize the main notations used in the paper.
      \begin{center}
   \begin{tabular}{|c|c|}
    \hline
     $(G,\cal R)$ & A Routed network \\
     \hline
      $\omega(u,v)$ & Weight of the arc $(u,v) \in A$ \\
      \hline
      $\lambda (u_i,r)$ & The latency of the vertex $u_i$ through $r$\\
         \hline
         $\lambda (r)$ & The latency of a route $r$.\\
         \hline
         $P$ & Period\\
         \hline
         $\tau$ & Size of a message\\
         \hline
         $ [t(v,r)]$&The set of time slots used by route $r$ at vertex $v$ \\
         & in a period $P$.\\
         \hline 
         ${\cal M}=(m_1, \ldots ,m_n)$&Offsets\\
    \hline

      \end{tabular}
      \end{center}

@@

      \begin{center}
      \includegraphics[width=\textwidth]{RRH.pdf}
      \end{center}

@@

       \begin{center}
      \includegraphics[width=\textwidth]{BBU.pdf}
      \end{center}

@@

       \begin{center}
	 \scalebox{0.8}{
\begin{tikzpicture}

@@

  \node[draw,circle] (cs) at (3, 2) {$c_s$}; 
  \node[draw,circle] (ct) at (5, 2) {$c_t$};

  \Edge[label = $\omega(s_1.c_s)$](s1)(cs)
  \Edge[label = $\omega(...)$](s2)(cs)
  \Edge[label = $\omega(...)$](s3)(cs)

  \Edge[label = $\omega(...)$](ct)(t1)
  \Edge[label = $\omega(...)$](ct)(t2)
  \Edge[label = $\omega(...)$](ct)(t3)

@@

	Finally, the time to build this assignment is dominated by the sorting of the routes from the longest to the shortest and is thus in $O(n\log(n)$.
     \end{proof}
\todo{Une remarque sur le fait que la complexite depend sans doute du nombre de valeurs differentes sur les arcs et pas du nombre de routes.}
